Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-13 paper.tex
Remove space
Clean up cl/cd explanation

Hydro- or airfoil section performance is generally characterized by the
lift-to-drag force ratio $L/D$  (or lift vs drag coefficient, $C_l/C_d$ ), which
is primarily a function of the foil's angle of attack $\alpha$. The angles of
attack for cross-flow turbine blades are a function of turbine tip speed ratio,
induction (slowing/turning of the free stream flow prior to reaching the
turbine), and turbine rotation or azimuthal angle $\theta$. Looking at static
airfoil data, we see that the static stall angle---the angle just beyond that at
which $L/D$ is maximum---increases with blade chord Reynolds number $Re_c$
\cite{Jacobs1937}.

>>>>

Hydro- or airfoil section performance is generally characterized by the
lift-to-drag force ratio $L/D$ (or the ratio of lift and drag coefficients,
$C_l/C_d$), which is primarily a function of the foil's angle of attack
$\alpha$. The angles of attack for cross-flow turbine blades are a function of
turbine tip speed ratio, induction (slowing/turning of the free stream flow
prior to reaching the turbine), and turbine rotation or azimuthal angle
$\theta$. Looking at static airfoil data, we see that the static stall
angle---the angle just beyond that at which $L/D$ is maximum---increases with
blade chord Reynolds number $Re_c$ \cite{Jacobs1937}.
